\section{The \framing{} Probe}
\label{sec:method}

\subsection{Problem Formulation}

Let a genre define a fixed set of $n$ generic Questions-Under-Discussion
$Q = \{q_1, \dots, q_n\}$, each carrying a human ground-truth importance $g_i \in [1,5]$
(the mean of $3$--$5$ annotator ratings). A model, prompted with $Q$ in some order, returns
a rating vector $\hat{r} \in [1,5]^n$, which induces a ranking. We study two things: (i)
how well $\hat{r}$ aligns with $g$ in a \emph{neutral} prompt, measured by \rhospear{}; and
(ii) how a single user opinion sentence about one target item $q_t$ shifts that item's rank.
Because the \quds are generic to the genre and not tied to a document the user could know
better, the opinion carries no legitimate information---any shift is framing-following, not
a Bayesian update.

\subsection{Ground Truth: Human Importance Annotations}

We repurpose the human importance annotations released by the \salience{}
project~\citep{trienes2025salience}. Each of four document genres has a shared set of \quds
that annotators rated $1$--$5$ for importance to a brief summary
(\tabref{tab:genres}). The genres span medical, computational-linguistics, astrophysics, and
meeting-transcript content, giving a deliberate diversity of domains.

We summarize the realistic upper bound on importance agreement with a \emph{human consensus
ceiling}: a leave-one-annotator-out \rhospear{} (each human against the mean of the others).
This ceiling is itself modest ($0.28$--$0.61$, mean $0.46$), reflecting that ``true''
priority is genuinely contested among humans---which is exactly why we score models against
the consensus rather than a perfect oracle.

\input{tables/genres}

\subsection{Framing Conditions}

For each genre we present the \quds---numbered, with order shuffled on every repeat to
control position bias---and ask for a $1$--$5$ importance rating per question, using the
\citet{trienes2025salience} introspection prompt. We compare three framings whose opinion
clauses are length- and tone-matched to one short sentence each, avoiding the
assertiveness/hedging confound flagged by \citet{shapira2026rlhf}:

\begin{itemize}[leftmargin=*,itemsep=1pt,topsep=2pt]
    \item \condN{} --- neutral, no user opinion.
    \item \condElow{} --- the user names a clearly \emph{low}-importance \qud{} as ``the
    single most important thing a summary must answer.''
    \item \condDtop{} --- the user dismisses a clearly \emph{top}-importance \qud{} as
    ``not really something a summary needs to answer.''
\end{itemize}

\subsection{Experiments}

\para{Exp 1 --- Priority knowledge.} We compute neutral \rhospear$(\hat{r}, g)$ per model
and genre and compare to the human ceiling. This establishes whether the model knows
consensus importance at all; without it, a framing shift would be uninterpretable.

\para{Exp 2 --- Priority sycophancy (headline).} For each framed elicitation we measure the
targeted item's shift versus the \emph{matched} neutral run (same model, genre, shuffle):
the rank shift \sycorank{} (positive $=$ moved toward the user) and the bounded $1$--$5$
rating shift \sycorating{}. The extreme-target design uses only emphasize-clearly-trivial
and dismiss-clearly-essential targets: $5$ models $\times$ $4$ genres $\times$ $(3{+}3$
targets$)$ $\times$ $4$ shuffles $=$ $480$ framed runs plus matched neutrals.

\para{Exp 3 --- Mechanism (does deference track uncertainty?).} We add $480$ \emph{mid-rank}
target runs and compute \compliance{}: the fraction of the \emph{available} shift actually
taken, which removes the position/room confound (a top item has little room to move up). We
bucket compliance by the target's ground-truth importance band (top / mid / bottom) and by
human disagreement, to test whether models reserve deference for genuinely ambiguous items.

\para{Exp 4 --- Arithmetic sycophancy (control).} We run the \citet{wei2023simple}
$a \times b$ probe with and without a ``math professor'' asserting a plausible wrong answer:
$5$ models $\times$ $120$ problems $\times$ $2$ conditions $=$ $1{,}200$ runs. This anchors
the priority results against a sycophancy signal with a verifiable ground truth, on the same
models.

\subsection{Models, Metrics, and Implementation}

\para{Models.} We use a capability gradient across four providers (via OpenRouter, June
2026): \llama{} (small open), \gptmini{} (small proprietary), \gemini{} (mid), and two
frontier models, \claude{} and \gptfive{}.

\para{Metrics.} Priority accuracy is \rhospear$(\hat{r}, g)$ (tie-aware, using average
ranks for the coarse $1$--$5$ scale). Sycophancy is the targeted-item \sycorank{} and
\sycorating{}, the follow-rate (fraction of framings moving the item the agreed way), and
\compliance{}. We also report the change in whole-ranking \rhospear$(\hat{r}, g)$ under
framing and the arithmetic accuracy drop. Confidence intervals come from $5{,}000\times$
bootstrap (seed $42$); we use paired Wilcoxon signed-rank tests against $0$ and
Mann-Whitney $U$ for group contrasts. \emph{All} models and genres are reported with no
selection.

\para{Implementation.} Priority elicitations use temperature $0.7$ with per-shuffle seeds
and $\geq 4$ order shuffles averaged; the arithmetic probe uses temperature $0.0$. The
\gptfive{} reasoning contract (\texttt{max\_completion\_tokens}, fixed temperature) is
handled in our harness. All $2{,}240$ API calls are cached on disk for exact
reproducibility, at a total cost of $\approx \$3.6$ ($\approx 451$k input $+$ $343$k output
tokens).
